Palomar 5 Gaps

### 2024-10-02 paper/main.tex
moved some methods to appendix

  Our study focuses on the influence of globular clusters on stellar streams, specifically examining whether globular clusters could produce gaps similar to those expected from dark matter subhalos. If globular clusters do indeed create such gaps, this factor must be considered when using stellar streams to detect dark matter. An additional and unique aspect of our study is that we focus on modeling real stellar streams and not just pure simulated streams. We focus on the Palomar 5 stream, which is well-studied, has observable gaps (bonaca et al 20XX), and is highly visible due to its position above the galactic disk. We present a result from one of our simulations in \ref{fig:stream_on_sky}, and the following sections describe our modeling of the stream, the gravitational interactions with the galaxy and other globular clusters, and the statistical analysis of perturbations affecting the stream.

@@

  \subsection{Numerical Methodology}
    Our numerical methodology follows the approach outlined in Ferrone et al. (2023), which we present here for completeness. We begin by extracting the phase space properties (positions, velocities) as well as the masses and half-mass radii of 165 globular clusters from the galactic globular cluster catalog by Baumgardt and Vasiliev et al. We handle the uncertainties through a monte-carlo approach. The catalog provides uncertainties for mass, distances, line of sight velocities, proper motions, with a covariance term between the proper motions. We repeate the whole experiment 50 times, for each of which we vary the initial conditions of each cluster by sampling its five-dimensional gaussian uncertaintiy distribution. However, for the first simulation, which we name \texttt{Sampling 000}, we use the most probable values for the initial conditions.

@@

    The primary methodological departure from Ferrone et al. (2023) is that now we include globular cluster interactions. Instead of treating the clusters as point masses that only experience the gravitational potential of the galaxy, we now compute N-body interactions between the clusters during the backward integration over 5 billion years. The equation of motion for the globular clusters is thus: 
    \begin{equation}
      \ddot{\vec{r}}_i = -\nabla \Phi(R_i,z_i) + \left.\sum_{j\neq i} \frac{Gm_j}{\left(|\vec{r}_j - \vec{r}_i|^2 + b_j^2\right)^{3/2}}\right. \left(\vec{r}_j - \vec{r}_i\right).
      \end{equation}\label{eq:GCNBody}
    Although these interactions were included, we observed no significant exchanges of orbital energy or momentum between clusters.

@@

    We then integrated the evolution of these particles forward in time to the present day. During this forward integration, each star particle feels the gravitational influence of the galaxy and all globular clusters, but not other star particles. We do not perform direct N-body simulations between star particles as in eq.~\ref{eq:GCNBody}; instead, at each time step, we load the positions of all globular clusters, as found from the initial integration, and apply their forces to the star particles. The equation of motion is thus: 
    \begin{equation}
      \ddot{\vec{r}}_p = -\nabla \Phi(R_p,z_p) + \left.\sum_{j} \frac{Gm_j}{\left(|\vec{r}_j(t) - \vec{r}_p|^2 + b_j^2\right)^{3/2}}\right. \left(\vec{r}_j(t)- \vec{r}_p\right).
      \end{equation} \label{eq:equation_of_motion_particle}

@@

    During the integration, intermediate snapshots were saved to facilitate the analysis of stellar streams and the effects of cluster impacts. Specifically, for each of the 50 realizations of the Palomar 5 stream, we saved $5000$ intermediate timesteps which is a temporal resolution of 1 million years. To provide an estimate of the size of our simulations, we have $N_p=100 000$, $N_\textrm{time stamps} = 5 000$, $N_\textrm{phase}=6$, $N_\textrm{sampling}=50$, and using single precision floating point numbers, $\textrm{Single}=4$~bytes, results in approximately 600 GB of data.

  \subsection{Gap detection} \label{sec:gap_detection}

@@

    To facilitate this process, we ran a series of \texttt{vanilla} simulations. In these control simulations, we used the same 50 sets of initial conditions but excluded interactions between globular clusters and omitted the gravitational influence of the clusters on the star particles within the stream. By comparing the morphological differences between these control simulations and the full simulations (which included cluster interactions), we could identify and assess the impact of globular clusters on the stream structure more effectively.

    Comparisons between the \texttt{vanilla} and full simulations were performed in the tail coordinate system. This system allows for consistent morphological comparisons by aligning the stream with the cluster's orbit. The coordinate system is based on the work of Dehnen et al. (2004) and is detailed in Appendix~\ref{appendix:TailCoordinates}.

    Briefly, the x' coordinate represents the position of a particle along the orbit relative to the globular cluster—whether it is ahead or behind the cluster. The y' coordinate measures the particle's distance within the orbital plane, where positive values indicate that the particle is farther from the Galactic center and negative values indicate that it is closer.

    \subsubsection*{Density Maps and Profiles}
      For each of the 50 simulations, we compare the final snapshots between the \texttt{vanilla} and \texttt{full} simulations using the tail coordinate system. We inspect these differences by generating 2D density maps of the streams. Additionally, we marginalize over the $y'$-coordinate to produce 1D density profiles along the $x'$-axis. These comparisons are shown in the results section (see Fig.~\ref{fig:profiles}).

@@

  \subsection*{Overview}
    This experiment follows a monte-carlo scheme, where we sample the initial conditions of the globular clusters' masses and kinematics based on their reported observational uncertainties and repeat the experiment multiple times. We choose to perform the simulation 50 times to balance computational and exploring a range of possible outcomes. The uncertainties on the globular clusters are large enough that over the course of the 5 Gyr integration period, they could be anywhere in their phase space given their initial energy and angular momentum. We inspected all simulations upon their completion and present one of them in in Fig.~\ref{fig:stream_on_sky}--which we selected for its clear and prominent gaps. Two of these gaps are visible in galactic coordinates and become even more apparent when marginalizing over latitutde to view it's 1D profile density over longitude.

    For each completed simulation, we follow the scheme laid out in the methods. I.e. we simulate the creation of the Palomar 5 stream for 50 different samplings of the initial conditions in two different environments. The first are the \texttt{vanilla} simulations in which the star-particles feel only the galaxy and Palomar 5. On the other hand, the \texttt{full} simulations includes the influence of all globualr clusters on the star-particles.

    By performing a comparative analysis, we are exploring the phenomenon of the influence from all globular clusters on stellar streams in a regieme of far more complete information respect to reality. In this experiment, we do not deal with differentiating stream and field stars, and above all else in reality we do not have a reference reality without the effect of other globular clusters as a point of comparison. Additionally, we avoid the difficulty of attempting to define a gap in its own right. Erkal et al 2015 was able to do this pretty well by studying two parameters: the width of the gaps and the ratio of the minimum density to the density of the gaps' shoulders. However, this becomes impossible when departing from the idealized case of uniformly dense \& one-dimensional streams on circular orbits. Sanders et al 2016 extended this in action-angle space which allowed for dropping the constraint of circular orbits. However, I need to revist the article again because I believe they also explored non uniformly dense streams. Nonetheless, we avoid this all together by doing our comparative analysis. Since we are numerical modellers, we can play god and run nearly the exact same experiment by including or not including the globular clusters. Therefore, it's much easier to identify what comes from the clusters or not.

    This comparative analysis is shown in Fig.~\ref{fig:profiles}. We visually compare the 2D density map in tail coordinates as well as their marginalized 1D density profiles along the length of Palomar 5's orbit. As described in section~\ref{sec:gap_detection}, we locate regions on the stream where the full simulations are significantly less dense than the vanilla simulations. We find that many gaps are visible by eye. However, some subtle under densities only became apparent when comparing the 1D density profiles. All simulations and labeled gaps are presented in the Appendix~\ref{appendix:gallery_of_gaps}.

    Subsequently, we followed the analysis presented in section~\ref{sec:SuspectToCulprit} to identify which globualr clusters were responsible for the gaps. This method used the orbit of Palomar 5 as a proxy for the stream. This is contrary to the typical case where one uses the stream to approximate the orbit--but $\approx$ works both ways. The gravitational force from all other globular clusters was computed at segments of the orbit about the position of Palomar 5 for the entire simulation. The top 5 strongest flybys were identified and the corresponding perturbers are labeled as \textit{suspects}. This is shown in Fig.~\ref{fig:force-on-orbit}, where the top panel shows the force from the globular clusters on the orbit, while the bottom panel shows the density of the stream. A density threshold was imparted to quantify the length of the stream. The location and time of impact was cross referenced to the location of the gaps to identify which cluster was responsible. I.e. if the gap was observed on the leading tail, we searched for suspects with $\tau>0$.

    The top panel of Fig.~\ref{fig:force-on-orbit} contains some interesting information. Notice the periodic ribbions of force in the $(t,\tau)$ plane. This is due to pericenter passages where Palomar 5 is getting closer to the center of mass of the globular cluster system. Additionally, for the impacts of NGC104 and NGC7078, wakes can be observed in the density map---evidence that signifies their guilt. Another important aspect, is that the strongest peak in gravitational force does not necessarily create a gap. Notice how NGC~5272, which was labeled with 0 to indicate that it has the greatest force of all local maxima, does not provoke a gap. The reason for this is manifold. First, remember that the important quantity is \textit{the change in momentum}. Thus, a strong force applied for a brief peroid of time may have no effect on the stream!  Additionally, there is an offset of about 200~pc between the stream at the orbit, as seen when viewing the stream in tail coordinates. This demonstrates that the orbit are good proxy's for the stream but are not a one for one substitute. We found that the top five greatest impacts accounted for all gaps, except for Sampling~014 as shown in Fig.~\ref{fig:gallery3}, whose gap from NGC~6584 corresponded to the 7th peak.

    For some cases, we performed a double check by launching extra simulations only including one suspect at a time to confirm that this suspect indeed caused a gap in question, an example is shown in Fig.~\ref{fig:decomposition}. Note that the gap from NGC~7078 was \textit{hit} by NGC~7078 \textit{twice}.

  \subsection*{Gap Morphology}
    We study the structure of the streams that have been impact by the globular clusters. The gallery of gaps is shown in the appendix, which includes the results from all of the simulations we considered in this experiment.

    In general, how did the passage of these globular clusters effect the stream? well. A lot of this has been studied quite well and presented in Sanders et al 2016. They even consdiered different types of impactors. I.e. impactors that had different density profiles. They compared Hernquist, Plummer, NFW, and a truncated NFW. There are some minor differences between the impactors however, the conclusion is still the same. Impacts from small and dense perturbers such as globular clusters only effect the stream locally.

    Our results are consistent with those shown previously. Perturber crossings only perturb the stream locally. Global characterisitcs of the stream do not change. For instance, the stream is not warmer of thicker. Other types of interactions have been demonstrated to do this. For example THIS AUTHOR showed that XXX and do YYY. As laid out in Erkal et al 2015, perturbers pull particles from the sides towards the impact point. These particles eventually move beyond the impact point and leave an under dense center and then pile up on the sides leaving an overdensity on the shoulders.

    Interestingly, most of our gaps occur for the leading tail. 8 on the trailing tail. 21 excluding NGC~2808 are on the leading tail. We have to exclude NGC~2808 because the simulations are clearly correlated with one another, so trials are not independent. So is 8/29 consistent with a fair coin toss? In anycase, we argue this may be a coincidence since being hit should only depend on the size and location of the stream. The main difference between the tails is a $\approx$ 300-400 pc offset in $r$, yet this is negligible.

    All of the gaps are oblique in tail coordinates. This is an artifact of using tail coordinates and arrises because we project the star-particles onto the nearest point of the orbit. (this is really difficult to explain with words and super simple with a picture. The picture being that we have three evenly spaced parallel lines that are close together. Then, a third point that is far away.  )

    Do our gaps grow linearly in time? what about this square root stuff?

    Lastly, since the streams have width, there are some instances where the stream is not significantly impact across this width. For instance, the gaps from NGC~5284 in Sampling 019 and NGC~6333 in Sampling 033 are more akin to bites than gaps.

@@

    The clusters that impacted Palomar 5's stream in our simulations are presented in Fig.~\ref{fig:histogram_impact_time}, along with when they impacted the stream. First, there are few impacts that happen early on in the simulation. This is not surprising, as it the tidal tails are smaller and thus there is less volume to be perturbed. Next, is that 44/50 simulations contain a visible gap from NGC2808, all of the encounters occuring about 200~Myr ago. This is so much more than any other peak that we broke the scale of the histogram so that this peak would not dwarf the significance of all others. The reason is that the uncertainty in the precise position of the clusters along their orbits grows in look back time. Since this encounter is recent, most of the sampled initial conditions give rise to a significant enough impact in the stream that causes a gap.

    \begin{figure*}
      \centering
      \includegraphics[width=\linewidth]{histogram_impact_time.png}
      \caption{The time of impact for each flyby that caused a gap. Each cluster is given a consistent and unique color. The scale of the histogram is broken between 8 and 42 since the gaps from NGC~2808 are in a league of their own with respect to other clusters.}
      \label{fig:histogram_impact_time}
      \end{figure*}

    We desire to search for some generalizable characterisitcs of the perturbers to see what contrasts them to globular clusters that do not impact the Pal5 Stream. We present three different graphs in Fig.~\ref{fig:mass_size_plane}. The top plot shows the angular momentm and energy plane. To no surprise, the globular clusters that perturb Palomar 5 are within a band of energy enclosed the energy of Palomar 5. This indicates that a cluster's orbital space needs to overlap with Palomar 5's. There appears not to be a preference in angular momentum. Note that in this panel all initial conditions for the clusters are plotted. Clusters of gray dots indicate the same cluster. However, for the least bound milky way clusters, the uncertainties in distances and motions allow for a wide range of energies, prograde and retrograde orbits. These are Crater, Palomar X and Eridanus. This is consistent with Vasiliev et al 2021, yet not very significant for this study since they do not influence Palomar 5 and could have been ignored.

    Next, in the middle panel of Fig.~\ref{fig:mass_size_plane} we view the mass size plane. The

@@

  \section{Impact Geometry Statistics}

>>>>

  Our study focuses on the influence of globular clusters on stellar streams, specifically examining whether globular clusters could produce gaps similar to those expected from dark matter subhalos. If globular clusters do indeed create such gaps, this factor must be considered when using stellar streams to detect dark matter. An additional and unique aspect of our study is that we focus on modeling real stellar streams and not just pure simulated streams. We focus on the Palomar 5 stream, which is well-studied, has observable gaps (bonaca et al 20XX), and is highly visible due to its position above the galactic disk. We present a result from one of our simulations in Fig.~\ref{fig:stream_on_sky}, and the following sections describe our modeling of the stream, the gravitational interactions with the galaxy and other globular clusters, and the statistical analysis of perturbations affecting the stream.

@@

  \subsection{Numerical Methodology}
    Our numerical methodology follows the approach outlined in Ferrone et al. (2023), which we present here for completeness. We begin by extracting the phase space properties (positions, velocities) as well as the masses and half-mass radii of 165 globular clusters from the galactic globular cluster catalog by Baumgardt and Vasiliev et al. We handle the uncertainties through a monte-carlo approach. The catalog provides uncertainties for mass, distances, line of sight velocities, proper motions and includes a covariance term between the proper motions. We repeate the whole experiment 50 times, for each of which we vary the initial conditions of each cluster by sampling its five-dimensional gaussian uncertaintiy distribution. However, for the first simulation, which we name \texttt{Sampling 000}, we use the most probable values for the initial conditions.

@@

    The primary methodological departure from Ferrone et al. (2023) is that now we include globular cluster interactions. Instead of treating the clusters as point masses that only experience the gravitational potential of the galaxy, we now compute N-body interactions between the clusters during the backward integration over 5 billion years. The equations of motion for the globular cluster system are thus: 
    \begin{equation}
      \ddot{\vec{r}}_i = -\nabla \Phi(R_i,z_i) + \left.\sum_{j\neq i} \frac{Gm_j}{\left(|\vec{r}_j - \vec{r}_i|^2 + b_j^2\right)^{3/2}}\right. \left(\vec{r}_j - \vec{r}_i\right),
    \end{equation}\label{eq:GCNBody} where $\vec{r}$ indicates the galacto-centric position, the index $i$ indicates a globular cluster of interest with $R_i,z_i$ being its galactocentric positions in cylindrical coordinates. The index $j$ indicates the other globular cluster that are summed over where: $m_j$ is its mass, $b_j$ is its plummer scale radius, and $r_j$ is it's galacto-centric position. $\Phi$ is the axis-symmteric potential of the model used for the Milky Way.

@@

    We then integrated the evolution of these particles forward in time to the present day. During this forward integration, each star particle feels the gravitational influence of the galaxy and all globular clusters, but not other star particles. We do not perform direct N-body simulations between star particles as in eq.~\ref{eq:GCNBody}; instead, at each time step, we load the positions of all globular clusters, as found from the initial integration, and apply their forces to the star particles. The equation of motion is thus: 
    \begin{equation}
      \ddot{\vec{r}}_p = -\nabla \Phi(R_p,z_p) + \left.\sum_{j} \frac{Gm_j}{\left(|\vec{r}_j(t) - \vec{r}_p|^2 + b_j^2\right)^{3/2}}\right. \left(\vec{r}_j(t)- \vec{r}_p\right),
      \end{equation} \label{eq:equation_of_motion_particle} where the index $p$ represents one of the 100,000 particles of interest.

@@

    During the integration, intermediate snapshots were saved to facilitate the analysis of stellar streams and the effects of cluster impacts. Specifically, for each of the 50 realizations of the Palomar 5 stream, we saved $5000$ intermediate timesteps which is a temporal resolution of 1 million years. To provide an estimate of the size of our simulations, we have $N_p=100 000$ number of particles, $N_\textrm{time stamps} = 5 000$ time steps, $N_\textrm{phase}=6$ phase space coordinates, $N_\textrm{sampling}=50$ monte-carlo samplings, and using single precision floating point numbers, $\textrm{Single}=4$~bytes. The product of the aforementioned terms results in approximately: $N_p=100 000 \times N_\textrm{time stamps}\times N_\textrm{phase}\times N_\textrm{sampling} 4 \textrm{bytes}\approx$ 600 GB of data.

  \subsection{Gap detection and Characterization} \label{sec:gap_detection}

@@

    To facilitate this process, we ran a series of \texttt{reference} simulations. In these control simulations, we used the same 50 sets of initial conditions but excluded interactions between globular clusters and omitted the gravitational influence of the clusters on the star particles within the stream--save for the host cluster Palomar 5. By comparing the morphological differences between these control simulations and the \texttt{full} simulations (which included cluster interactions), we could identify and assess the impact of globular clusters on the stream structure more effectively.

    Comparisons between the \texttt{reference} and \texttt{full} simulations were performed in the tail coordinate system. This system allows for consistent morphological comparisons by aligning the stream with the cluster's orbit. The coordinate system is based on the work of Dehnen et al. (2004) and is detailed in Appendix~\ref{appendix:TailCoordinates}. Briefly, the x' coordinate represents the position of a particle along the orbit relative to the globular cluster—whether it is ahead or behind the cluster. The y' coordinate measures the particle's distance within the orbital plane, where positive values indicate that the particle is farther from the Galactic center and negative values indicate that it is closer.

    More details on how the gaps and corresponding perturbing globular clusters were identified is provided in Appendix.~XXX. A first order approach of understanding the significance of an impact one needs to compute its change in momentum, which is determined by integrating the force acting on the particle over the duration of the interaction. A useful approximation for this change in momentum is the force at the closest approach multiplied by an estimate of the interaction time:
    \begin{equation} 
      \Delta v \approx \text{Force} \times \text{interaction time} = \frac{GM}{b^2} \times 2\frac{b}{v} = 2\frac{GM}{bv}, 
      \end{equation} \label{eq:change_in_momentum}
    where $M$ is the mass of the perturber, $m$ is the mass of the particle, $b$ is the impact parameter, $v$ is the relative velocity of the perturber with respect to the particle, and $G$ is the gravitational constant. We compute this for the top five cloestest approaches of all globular clusters on an orbital segment about Palomar 5 that approximates the stream through out each of the 50 simulations. In the end, we have a sample of 250 impacts and compare the impact geometry of those that cause gaps to those that do not.

  \subsection*{Overview}

    Although these interactions were included, we observed no significant exchanges of orbital energy or momentum between clusters.

    This experiment follows a monte-carlo scheme, where we sample the initial conditions of the globular clusters' masses and kinematics based on their corresponding uncertainties and then repeat the experiment multiple times. We choose to perform the simulation 50 times to balance computational cost with a high enough number to allow us to explore a range of possible outcomes. The uncertainties on the globular clusters are large enough that over the course of the 5 Gyr integration period, they could be anywhere allowed in their phase space given their initial energy and angular momenta. We inspected all simulations upon their completion and present one of them in in Fig.~\ref{fig:stream_on_sky}--which we selected for its clear and prominent gaps. Two of these gaps are visible in galactic coordinates and become even more apparent when marginalizing over latitutde to view it's 1D profile density over longitude.

    For each completed simulation, we follow the scheme laid out in the methods. I.e. we simulate the creation of the Palomar 5 stream for 50 different samplings of the initial conditions, with two different cases. The \textit{Full} simulation that includes the influence of all globualr clusters on the star particles representing Palomar 5 and its stream, as well as the \textit{vanilla} simulations in which the star-particles feel only the galaxy and Palomar 5. We do this for we attempt to quantify the number of gaps from globular clusters in the limit of maximum information. I.e. we are not limited by contamination of field stars, and since we are computing our own simulations, we know what a gapless stream should look like.

    This comparative analysis is shown in Fig.~\ref{fig:profiles}. We visually compare the 2D density map in tail coordinates as well as their marginalized 1D density profiles along the length of Palomar 5's orbit. As described in section~\ref{sec:gap_detection}, we locate regions on the stream where the full simulations are significantly less dense than the vanilla simulations. We find that many streams as visible by eye. However, some subtle under densities only became apparent when comparing the 1D density profiles. All simulations and labeled gaps are presented in the Appendix~\ref{appendix:gallery_of_gaps}.

    Subsequently, we followed the analysis presented in section~\ref{sec:SuspectToCulprit} to identify which globualr clusters were responsible for the gaps. This method used the orbit of Palomar 5 as a proxy for the stream. The gravitational force from all other globular clusters as computed at segments of the orbit about the position of Palomar 5 for the entire simulation. The top 5 strongest flybys were recorded to identify which cluster was responsible. This is shown in Fig.~\ref{fig:force-on-orbit}, where the top panel shows the force from the globular clusters on the orbit, while the bottom panel shows the density of the stream. A density threshold was imparted to quantify the length of the stream.  The location and time of impact was cross referenced to the location of the gaps to identify which cluster was responsible.

    Fig.~\ref{fig:force-on-orbit} contains some interesting information. Notice the periodic ribbions of force in the $(t,\tau)$ plane. This is due to pericenter passages where Palomar 5 is getting closer to the center of mass of the globular cluster system. Additionally, for the impacts of NGC104 and NGC7078, wakes can be observed in the density map. Another important aspect, is that the strongest peak in gravitational force does not necessarily create a gap. Notice how NGC5272, which was labeled with 0 to indicate that it has the greatest local maxima does not have a gap. This is manifold, for instance, the force needs to be modulated with the time of impact because the  important quantity that determins gap creation.  Additionally, there is an offset of about 200~pc between the stream at the orbit, as seen when viewing the stream in tail coordinates, so peaks upon the orbit are good proxy's for the stream but are not definitive. We found that the top five greatest impacts accounted for all gaps, except for Sampling~014 as shown in Fig.~\ref{fig:gallery3}, whose gap from NGC~6584 corresponded to the 7th peak.

    For some cases, we performed a double check by launching extra simulations only including one suspect at a time to confirm that this suspect indeed caused a gap in question, an example is shown in Fig.~\ref{fig:decomposition}. Note that the gap from NGC~7078 was \textit{hit twice}.

@@

 \subsection*{Gap Morphology}

@@

  The clusters that impacted Palomar 5's stream in our simulations are presented in Fig.~\ref{fig:histogram_impact_time}, along with when they impacted the stream. First, there are few impacts that happen early on in the simulation. This is not surprising, as it the tidal tails are smaller and thus there is less volume to be perturbed. Next, is that 44/50 simulations contain a visible gap from NGC2808, all of the encounters occuring about 200~Myr ago. This is so much more than any other peak that we broke the scale of the histogram. The reason is that the uncertainty in the precise position of the clusters along their orbits grows in look back time. Since this encounter is recent, most of the sampled initial conditions give rise to a significant enough impact in the stream that causes a gap.

  \begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{histogram_impact_time.png}
    \caption{When the impacts occured}
    \label{fig:histogram_impact_time}
    \end{figure*}

    We desire to search for some generalizable characterisitcs of the perturbers to see what contrasts them to globular clusters that do not impact the Pal5 Stream. We present three different graphs in Fig.~\ref{fig:mass_size_plane}. The top plot shows the angular momentm and energy plane. The

    - to no surprise, you have to come within Palomar 5's orbital space

@@

  \section{Gap detection and characterization methods}
    \subsubsection*{Density Maps and Profiles}
      For each of the 50 simulations, we compare the final snapshots between the \texttt{vanilla} and \texttt{full} simulations using the tail coordinate system. We inspect these differences by generating 2D density maps of the streams. Additionally, we marginalize over the $y'$-coordinate to produce 1D density profiles along the $x'$-axis. These comparisons are shown in the results section (see Fig.~\ref{fig:profiles}).
